Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-07 Manuscript.Rmd
Added supplemental materials area

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  word_document: 
    reference_docx: Style_reference.docx
  pdf_document: default
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

  # This part is just for reference, as the labels are loaded from a file
  # # Retain only the significant parcels
  # t1 <- valCounts$Label[valCounts$pVal < 0.05]
  # t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
  # 
  # # Remove hemispheric references 
  # t1 <- unique(substring(t1,2))
  # t2 <- unique(substring(t2,2))
  # 
  # # And get the set of overlapping areas between literatures
  # # This is missing some cingulate and PFC areas, and adds V2.
  # # However, we can say that we are filling in the gap for completeness,
  # # and removing V2 because it's demonstrably irrelevant.
  # bothLbls_alt <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
  # 
  # # You could also try to permute the allocation of reports per literature,
  # # and then perform a chi-squared per parcel. Get the max stat per iteration.
  # # Now you have your null distribution.
```

@@

Figure 1 shows the resulting ROIs from these analyses. As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all p < 0.05). A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function. Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, p < 0.001).

@@

>>>>

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
  pdf_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

  # Retain only the significant parcels
  t1 <- valCounts$Label[valCounts$pVal < 0.05]
  t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]

  # Remove hemispheric references
  t1 <- unique(substring(t1,2))
  t2 <- unique(substring(t2,2))

  # Labels to put in text
  dmnLbls <- gsub("ROI","", t2) 
  dmnLbls <- gsub("_","", dmnLbls)
  valLbls <- gsub("ROI","", t1) 
  valLbls <- gsub("_","", valLbls)

  # This part is just for reference, as the labels are loaded from a file
  # # And get the set of overlapping areas between literatures
  # # This is missing some cingulate and PFC areas, and adds V2.
  # # However, we can say that we are filling in the gap for completeness,
  # # and removing V2 because it's demonstrably irrelevant.
  # bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
  # 
  # # You could also try to permute the allocation of reports per literature,
  # # and then perform a chi-squared per parcel. Get the max stat per iteration.
  # # Now you have your null distribution.

@@

Figure 1 shows the resulting ROIs from these analyses. DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1). As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all p < 0.05). A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function. Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, p < 0.001).

@@

## Supplemental Materials

### *Table 1. Significant brain regions per literature*
| Literature                     | Significant Brain Regions      |
| :----------------------------- | -----------------------------: |
| Default Mode Network           | `r paste(dmnLbls)`             |
| Subjective Value               | `r paste(valLbls)`             |
